Robust Spectroscopic Inference with Imperfect Models

### 2014-09-10 tex/paper.tex
Removed reset after burn in

The elements of the interpolation covariance matrix $\mathsf{C}_{ij}^\textrm{int}$ are determined empirically from the drop-out spectra, and are a function of the degree of the interpolation.

\begin{equation}
  \mathsf{C}_{ij}^\textrm{int} = 
\end{equation}

>>>>

The elements of the interpolation covariance matrix $\mathsf{C}_{ij}^\textrm{int}$ are determined empirically from the drop-out spectra, and are a function of the degree of the interpolation. The variables are notated such that the last index changes most rapidly.

We could represent the average covariance matrix, for a specific axis $k$, completed from all of the grid points as

\begin{equation}
  \mathsf{C}_{ijk}^\textrm{int} = \sum_{l=1}^8  b_{kl} \lambda_{ikl} \lambda_{jkl}
\end{equation}
Then, the final combined matrix requires some weighting based upon interpolation distance in each of the three axes, $k$
\begin{equation}
  \mathsf{C}_{ij}^\textrm{int} = w_{ij}(r_0) \sum_{k=1}^3 a_k \mathsf{C}_{ijk}^\textrm{int}
\end{equation}
We also add in a Hann taper to ensure sparsity of the covariance matrix for computational efficiency, however note that the interpolation error covariance matrix is itself dense.

Here, $b_{kl}$ corresponds to the same weights that would be applied to each spectra in the interpolation case, for a specific axis $k$. The estimate of covariance is determined as a weighted average between the covariance matrices at all of the grid points.

Then, the final covariance
